Deliminative verbal reduplication in Mandarin Chinese

### 2024-09-30 chapters/ch01-Intro.tex
spacing

In Mandarin Chinese, verbs can be reduplicated to express a delimitative aspectual meaning (e.g. \citealt[204--205]{Chao1968}; \citealt[232]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec. 4.3]{XiaoMcEnery2004}). 
This means that the event or state denoted by the verb happens in a short duration and/or a low frequency \citep[155]{XiaoMcEnery2004}, such as illustrated in (\ref{ex:redup-ex}).\footnote{Reduplications
    in the example sentences will be set in italics.}
Thus, verbal reduplication in Mandarin Chinese is often translated as doing something ``a little bit/for a little while''.

@@

	\ex
	\gll \objex{qing3} \objex{ni3} \obj{chang2}-\objex{chang} \objex{zhe4} \objex{dao4} \objex{cai4}.\\
	please you taste-taste this \textsc{clf} dish\\
	\glt `Please taste this dish a little bit.' 
	\z
\z

>>>>

In Mandarin Chinese, verbs can be reduplicated to express a delimitative aspectual meaning (e.g. \citealt[204--205]{Chao1968}; \citealt[232]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec.\,4.3]{XiaoMcEnery2004}). 
This means that the event or state denoted by the verb happens in a short duration and/or a low frequency \citep[155]{XiaoMcEnery2004}, such as illustrated in (\ref{ex:redup-ex}).\footnote{Reduplications
    in the example sentences will be set in italics.}
Thus, verbal reduplication in Mandarin Chinese is often translated as doing something ``a little bit/for a little while''.

@@

	\ex
	\gll \objex{qing3} \objex{ni3} \obj{chang2}-\obj{chang} \objex{zhe4} \objex{dao4} \objex{cai4}.\\
	please you taste-taste this \textsc{clf} dish\\
	\glt `Please taste this dish a little bit.' 
	\z
\z

### 2024-09-30 chapters/ch02-Phenomenon.tex
spacing

 \citet{Fan1964}, \citet{Arcodiaetal2014}  and \citet{Xie2020} compare the AA, ABAB and AABB forms of reduplication 
and found a number of differences between the AA, ABAB forms compared to the AABB form in terms of their semantics, productivity, syntactic distribution and origin. 
Specifically, \citet[17--18]{Arcodiaetal2014}, \citet[144]{MelloniBasciano2018} and \citet[90]{Xie2020} identify that AA and ABAB have a diminishing meaning, 
namely that the event happens for a short duration or to a small extent. 
By contrast, AABB expresses an increasing meaning, which indicates a repetition or an action in progress. 
\citet[Sec. 3.1]{Xie2020} also finds that AA and ABAB have relatively high productivity, 
whereas the productivity of AABB is low. 
She further shows that AABB is generally correlated with the lack of a postverbal object, but the direct object remains present when a transitive verb undergoes AA or ABAB patterns of reduplication. 
\citet[277]{Fan1964} proposes that AA, ABAB originated from the verb-measure word combination from Middle Chinese, 
while AABB developed from the reiterative rhetoric from Old Chinese. 
These differences seem to suggest that there is a fundmental difference between these two groups of verbal reduplication. 
The current study will only focus on the AA, A-\textit{yi}-A, A-\textit{le}-A, A-\textit{le}-\textit{yi}-A, ABAB and AB-\textit{le}-AB forms of verbal reduplication in Mandarin Chinese.
AA-\obj{kan4}, A-\obj{kan4}-\obj{kan4}, AAB, A-\textit{yi}-AB, A-\textit{le}-AB will also be mentioned occasionally to provide further arguments.
In what follows, the term \textit{reduplication} will be used  to refer specifically to the AA, A\hyp{}\textit{yi}\hyp{}A, A-\textit{le}-A, A-\textit{le}-\textit{yi}-A, ABAB and AB-\textit{le}-AB forms, if not specified otherwise.

@@

The reduplication has a \textit{delimitativeness} meaning (e.g.\ \citealt[204--205]{Chao1968}; \citealt[232]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec. 4.3]{XiaoMcEnery2004}). 
To be specific, the reduplication of [$+$durative] verbs reduces the duration of the events,
and the reduplication of [$-$durative] verbs reduces the iteration frequency of the events \citetext{\citealp[14]{Li1996}; \citealp[149--150]{XiaoMcEnery2004}}.
Besides delimitativeness, \citet[204]{Chao1968}, \citet[276]{Fan1964}, \citeauthor{Smith1991} (\citeyear[356]{Smith1991}; \citeyear[199--120]{Smith1994}), \citet[14]{Li1996} and \citet[290--291]{Tsao2001} suggest that the reduplication signifies \textit{tentativeness}, which can be used
``to refer modestly to one's own activities, or for mild imperatives'' \citep[356]{Smith1991}, or ``trying to'' do something \citep[234]{LiThompson1981}.
\textit{Frequentativeness} or \textit{habitualness}, that the event denoted by the verb happens frequently or habitually, is mentioned by \citet[276]{Fan1964}, \citet[15]{Li1996} and \citet[1]{Qian2000} as the meaning of reduplication as well.
 \citet[276]{Fan1964} further proposes a meaning of \textit{slightness} or \textit{casualness} for reduplication, which implies that the event is unimportant or conveys a casual attitude of the speaker.
 \citet[Sec. 3.1.3]{Zhu1998} suggests that the main function of reduplication is to \textit{increase the agency} of the action or the change denoted by the verb.

@@

As for A-\textit{yi}-A, \citet[273]{Fan1964} compares examples found in novels and plays and concludes that A-\textit{yi}-A has exactly the same meaning as its AA counterpart.
She thus assumed that AA is merely a form of A-\textit{yi}-A, where the \textit{yi} is omitted phonologically.
\citet[Sec. 5]{Xing2000} considers that the major  difference  between AA and A-\textit{yi}-A lies in the speaker's attitude.
The former conveys a casual attitude whereas the latter sounds more serious. %\footnote{This can be a register effect. Register project sponsorship xxxxxxx}
However, he stresses that there is no difference in the delimitative semantics of both forms,
and that the variance in meaning is a pragmatic one.
The difference is also not absolute and often only shows a tendency.
\citet{Xu2002} finds out that compared to A-\textit{yi}-A, one tends to use AA in contexts with strong emotional attitudes, urgent, casual, timid or uncertain contexts.
But he also states that these differences are pragmatic rather than semantic, 
as he argues that AA and A-\textit{yi}-A can be used interchangeably in most cases,
and the differences in meaning only arise from specific contexts as a whole.
\citet[15]{Yang2003} suggests that AA and A-\textit{yi}-A have the same core meaning, while A-\textit{yi}-A implies a slightly more serious attitude than AA due to its length.
We assume A-\textit{yi}-A to be a form of reduplication and that it has the same core semantics as AA.

@@

On the other hand, as the reviewer %\citealt[283]{Ding2010}, \citealt[fn. 3]{BascianoMelloni2017}
and indeed \citet[669--670]{Tham2013} herself noted,
verbs expressing psychological states such as these can have a COS interpretation (but not necessarily),
let us look at other examples of stative verbs listed by \citet[680]{PeckEtAl2013} which do not express psychological states,
and examples in  \citet[Sec. 3.3.3]{XiaoMcEnery2004} of individual-level states (ILSs) which only have stative interpretation,
as opposed to stage-level states (SLSs) which can have both stative and dynamic interpretations.\footnote{
    Note that most examples of ILSs in \citet[Sec. 3.3.3]{XiaoMcEnery2004} are adjectives.
    Since in Mandarin Chinese, adjectives have a different reduplication pattern (see e.g.\ \citealt[Sec. 2.2]{Tsao2001}, \citealt[Sec. 4.1]{FanSongBond2015}, \citealt[Sec. 3]{Sui2018}),
    and further, COS verbs can be systematically derived from adjectives \citep[Sec. 3]{Tham2013},
    these predicates are not included in our examples.}
The following examples contain the reduplication of \obj{xiang4} `look like' and \obj{zai4-chang3} `be present on the scene'.
\ea\label{ex:xiang}%范丞丞雪中撑伞这是蒋丞吧王圣迪也拿着滑板！太像顾淼了王安宇你快点也像一像吧！(https://www.163.com/dy/article/FS1FKUC30534DZO1.html (2020/11/22, accessed 2024/03/26))
Context: \objex{Wang2} \objex{Sheng4di2} is the actor of the character \objex{Gu4} \objex{Miao3} in a TV series.
\objex{Wang2} Ān\objex{yu3} is another actor in the series.\\
\\
\gll \objex{Wang2} \objex{Sheng4di2} \ldots\, \objex{tai4} \objex{xiang4} \objex{Gu4} \objex{Miao3} \objex{le}. \objex{Wang2} Ān\objex{yu3} \objex{ni3} \objex{kuai4dian3} \objex{ye3} \obj{xiang4-yi-xiang4} \objex{ba}!\footnotemark\\
Wang Shengdi {} very look.like Gu Miao \textsc{ptc} Wang Anyu you fast also look.like-one-look.like \textsc{ptc}\\
\glt `Wang Shengdi \ldots\,  really looks like Gu Miao. Wang Anyu, you too should just look like (your character) already!'

@@

The literature on reduplication makes different assumptions on whether it is a morphological or syntactic phenomenon.
\citet[Ch. 4]{Chao1968}, \citet[Ch. 3]{LiThompson1981}, \citet[Sec. 4.1]{Dai1992} and \citet[4--5]{Liao2014} list reduplication under morphological processes. 
By contrast, \citet[23]{Arcodiaetal2014}, \citet{Xiong2016}, \citet[146]{BascianoMelloni2017}, \citet[229--231]{YangWei2017}, \citet[330]{MelloniBasciano2018} and \citet{Xie2020}  claim it to be syntactic.
%And e.g. \citet{Chen2001}, \citet{Chen2005}  and \citet{Yang2003} did not make any claim about its grammatical status.
This section reviews the arguments in \citet{Xie2020},
and applies tests from \citeauthor{Dai1992} (\citeyear[Sec. 7]{Dai1992}, \citeyear[Sec. 2.3--2.4]{Dai1998}) to distinguish words from phrases in Mandarin Chinese.
 %applies the tests proposed by \citet{Duanmu1998} and \citet{Schaefer2009} to distinguish words from phrases in Mandarin Chinese 
%and compares the behaviors of the reduplication with those of Parallel Verb Compounds 
%(compounds which consist of two verbs that ``either are synonymous or signal the same type of predicative notions'' \citep[68]{LiThompson1981}, e.g. \textit{gou-mai} `purchase-buy, buy') and {SVC}s. 
The results are compatible with a lexical analysis.

@@

In any case, since reduplication is not compounding (\citealt[149--150]{Sui2018}; \citealt{GaoEtAl2021} provides psycholinguistic evidence),
and the patterns discussed here constitute a different process than the AABB pattern
(see the discussions above, also \citealt[Sec. 4.3]{Deng2013}, \citealt[Sec. 2]{SuiHu2016}, \citealt{Sui2018} and \citealt{Wang2023}),
it is not surprising that \obj{le} occurs at a different position.

>>>>

 \citet{Fan1964}, \citet{Arcodiaetal2014}  and \citet{Xie2020} compare the AA, ABAB and AABB forms of reduplication 
and found a number of differences between the AA, ABAB forms compared to the AABB form in terms of their semantics, productivity, syntactic distribution and origin. 
Specifically, \citet[17--18]{Arcodiaetal2014}, \citet[144]{MelloniBasciano2018} and \citet[90]{Xie2020} identify that AA and ABAB have a diminishing meaning, 
namely that the event happens for a short duration or to a small extent. 
By contrast, AABB expresses an increasing meaning, which indicates a repetition or an action in progress. 
\citet[Sec.\,3.1]{Xie2020} also finds that AA and ABAB have relatively high productivity, 
whereas the productivity of AABB is low. 
She further shows that AABB is generally correlated with the lack of a postverbal object, but the direct object remains present when a transitive verb undergoes AA or ABAB patterns of reduplication. 
\citet[277]{Fan1964} proposes that AA, ABAB originated from the verb-measure word combination from Middle Chinese, 
while AABB developed from the reiterative rhetoric from Old Chinese. 
These differences seem to suggest that there is a fundmental difference between these two groups of verbal reduplication. 
The current study will only focus on the AA, A-\textit{yi}-A, A-\textit{le}-A, A-\textit{le}-\textit{yi}-A, ABAB and AB-\textit{le}-AB forms of verbal reduplication in Mandarin Chinese.
AA-\obj{kan4}, A-\obj{kan4}-\obj{kan4}, AAB, A-\textit{yi}-AB, A-\textit{le}-AB will also be mentioned occasionally to provide further arguments.
In what follows, the term \textit{reduplication} will be used  to refer specifically to the AA, A\hyp{}\textit{yi}\hyp{}A, A-\textit{le}-A, A-\textit{le}-\textit{yi}-A, ABAB and AB-\textit{le}-AB forms, if not specified otherwise.

@@

The reduplication has a \textit{delimitativeness} meaning (e.g.\ \citealt[204--205]{Chao1968}; \citealt[232]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec.\,4.3]{XiaoMcEnery2004}). 
To be specific, the reduplication of [$+$durative] verbs reduces the duration of the events,
and the reduplication of [$-$durative] verbs reduces the iteration frequency of the events \citetext{\citealp[14]{Li1996}; \citealp[149--150]{XiaoMcEnery2004}}.
Besides delimitativeness, \citet[204]{Chao1968}, \citet[276]{Fan1964}, \citeauthor{Smith1991} (\citeyear[356]{Smith1991}; \citeyear[199--120]{Smith1994}), \citet[14]{Li1996} and \citet[290--291]{Tsao2001} suggest that the reduplication signifies \textit{tentativeness}, which can be used
``to refer modestly to one's own activities, or for mild imperatives'' \citep[356]{Smith1991}, or ``trying to'' do something \citep[234]{LiThompson1981}.
\textit{Frequentativeness} or \textit{habitualness}, that the event denoted by the verb happens frequently or habitually, is mentioned by \citet[276]{Fan1964}, \citet[15]{Li1996} and \citet[1]{Qian2000} as the meaning of reduplication as well.
 \citet[276]{Fan1964} further proposes a meaning of \textit{slightness} or \textit{casualness} for reduplication, which implies that the event is unimportant or conveys a casual attitude of the speaker.
 \citet[Sec.\,3.1.3]{Zhu1998} suggests that the main function of reduplication is to \textit{increase the agency} of the action or the change denoted by the verb.

@@

As for A-\textit{yi}-A, \citet[273]{Fan1964} compares examples found in novels and plays and concludes that A-\textit{yi}-A has exactly the same meaning as its AA counterpart.
She thus assumed that AA is merely a form of A-\textit{yi}-A, where the \textit{yi} is omitted phonologically.
\citet[Sec.\,5]{Xing2000} considers that the major  difference  between AA and A-\textit{yi}-A lies in the speaker's attitude.
The former conveys a casual attitude whereas the latter sounds more serious. %\footnote{This can be a register effect. Register project sponsorship xxxxxxx}
However, he stresses that there is no difference in the delimitative semantics of both forms,
and that the variance in meaning is a pragmatic one.
The difference is also not absolute and often only shows a tendency.
\citet{Xu2002} finds out that compared to A-\textit{yi}-A, one tends to use AA in contexts with strong emotional attitudes, urgent, casual, timid or uncertain contexts.
But he also states that these differences are pragmatic rather than semantic, 
as he argues that AA and A-\textit{yi}-A can be used interchangeably in most cases,
and the differences in meaning only arise from specific contexts as a whole.
\citet[15]{Yang2003} suggests that AA and A-\textit{yi}-A have the same core meaning, while A-\textit{yi}-A implies a slightly more serious attitude than AA due to its length.
We assume A-\textit{yi}-A to be a form of reduplication and that it has the same core semantics as AA.

@@

On the other hand, as the reviewer %\citealt[283]{Ding2010}, \citealt[fn. 3]{BascianoMelloni2017}
and indeed \citet[669--670]{Tham2013} herself noted,
verbs expressing psychological states such as these can have a COS interpretation (but not necessarily),
let us look at other examples of stative verbs listed by \citet[680]{PeckEtAl2013} which do not express psychological states,
and examples in  \citet[Sec.\,3.3.3]{XiaoMcEnery2004} of individual-level states (ILSs) which only have stative interpretation,
as opposed to stage-level states (SLSs) which can have both stative and dynamic interpretations.\footnote{
    Note that most examples of ILSs in \citet[Sec.\,3.3.3]{XiaoMcEnery2004} are adjectives.
    Since in Mandarin Chinese, adjectives have a different reduplication pattern (see e.g.\ \citealt[Sec.\,2.2]{Tsao2001}, \citealt[Sec.\,4.1]{FanSongBond2015}, \citealt[Sec.\,3]{Sui2018}),
    and further, COS verbs can be systematically derived from adjectives \citep[Sec.\,3]{Tham2013},
    these predicates are not included in our examples.}
The following examples contain the reduplication of \obj{xiang4} `look like' and \obj{zai4-chang3} `be present on the scene'.
\ea\label{ex:xiang}%范丞丞雪中撑伞这是蒋丞吧王圣迪也拿着滑板！太像顾淼了王安宇你快点也像一像吧！(https://www.163.com/dy/article/FS1FKUC30534DZO1.html (2020/11/22, accessed 2024/03/26))
Context: \objex{Wang2} \objex{Sheng4di2} is the actor of the character \objex{Gu4} \objex{Miao3} in a TV series.
\objex{Wang2} Ān\objex{yu3} is another actor in the series.\\
\\
\gll \objex{Wang2} \objex{Sheng4di2} \ldots\, \objex{tai4} \objex{xiang4} \objex{Gu4} \objex{Miao3} \objex{le}. \objex{Wang2} Ān\objex{yu3} \objex{ni3} \objex{kuai4dian3} \objex{ye3} \obj{xiang4-yi-xiang4} \objex{ba}!\footnotemark\\
Wang Shengdi {} very look.like Gu Miao \textsc{ptc} Wang Anyu you fast also look.like-one-look.like \textsc{ptc}\\
\glt `Wang Shengdi \ldots\,  really looks like Gu Miao. Wang Anyu, you too should just look like (your character) already!'

@@

The literature on reduplication makes different assumptions on whether it is a morphological or syntactic phenomenon.
\citet[Ch. 4]{Chao1968}, \citet[Ch. 3]{LiThompson1981}, \citet[Sec.\,4.1]{Dai1992} and \citet[4--5]{Liao2014} list reduplication under morphological processes. 
By contrast, \citet[23]{Arcodiaetal2014}, \citet{Xiong2016}, \citet[146]{BascianoMelloni2017}, \citet[229--231]{YangWei2017}, \citet[330]{MelloniBasciano2018} and \citet{Xie2020}  claim it to be syntactic.
%And e.g. \citet{Chen2001}, \citet{Chen2005}  and \citet{Yang2003} did not make any claim about its grammatical status.
This section reviews the arguments in \citet{Xie2020},
and applies tests from \citeauthor{Dai1992} (\citeyear[Sec.\,7]{Dai1992}, \citeyear[Sec.\,2.3--2.4]{Dai1998}) to distinguish words from phrases in Mandarin Chinese.
 %applies the tests proposed by \citet{Duanmu1998} and \citet{Schaefer2009} to distinguish words from phrases in Mandarin Chinese 
%and compares the behaviors of the reduplication with those of Parallel Verb Compounds 
%(compounds which consist of two verbs that ``either are synonymous or signal the same type of predicative notions'' \citep[68]{LiThompson1981}, e.g. \textit{gou-mai} `purchase-buy, buy') and {SVC}s. 
The results are compatible with a lexical analysis.

@@

In any case, since reduplication is not compounding (\citealt[149--150]{Sui2018}; \citealt{GaoEtAl2021} provides psycholinguistic evidence),
and the patterns discussed here constitute a different process than the AABB pattern
(see the discussions above, also \citealt[Sec.\,4.3]{Deng2013}, \citealt[Sec.\,2]{SuiHu2016}, \citealt{Sui2018} and \citealt{Wang2023}),
it is not surprising that \obj{le} occurs at a different position.

### 2024-09-30 chapters/ch04-Previous.tex
spacing

Nevertheless, this analysis has some shortcomings.
To begin with, since the combination with aspect markers is completely forbidden, it is impossible for this approach to account for A\hyp{}\textit{le}\hyp{}A.
Moreover, as verbal reduplication is  considered to express a delimitative aspectual meaning,
it seems unconvincing to assume that there is no aspect information in its semantics.
We consider a semantic explanation as described in  \sectref{sec:aspM} to be more reasonable for ruling out aspect markers other than \textit{le}.
Furthermore, this account can only deal with monosyllabic reduplication and handles ABAB and AAB as irregular forms, for the reason that ABAB and AAB reduplication of AB verbs ``are not very productive in Chinese'' \citep[102]{FanSongBond2015}.
This is not true. 
\citet[33]{Xing2000stat}, \citet[161]{BascianoMelloni2017}, \citet[329]{MelloniBasciano2018} and  \citet[Sec. 3.1]{Xie2020}  all consider both AA and ABAB to be productive,
and \citet[36]{Xing2000stat} concludes that AAB is productive as well.
Thus, these forms should not be handled as  irregular forms, but should be derivable by lexical rules.

>>>>

Nevertheless, this analysis has some shortcomings.
To begin with, since the combination with aspect markers is completely forbidden, it is impossible for this approach to account for A\hyp{}\textit{le}\hyp{}A.
Moreover, as verbal reduplication is  considered to express a delimitative aspectual meaning,
it seems unconvincing to assume that there is no aspect information in its semantics.
We consider a semantic explanation as described in  \sectref{sec:aspM} to be more reasonable for ruling out aspect markers other than \textit{le}.
Furthermore, this account can only deal with monosyllabic reduplication and handles ABAB and AAB as irregular forms, for the reason that ABAB and AAB reduplication of AB verbs ``are not very productive in Chinese'' \citep[102]{FanSongBond2015}.
This is not true. 
\citet[33]{Xing2000stat}, \citet[161]{BascianoMelloni2017}, \citet[329]{MelloniBasciano2018} and  \citet[Sec.\,3.1]{Xie2020}  all consider both AA and ABAB to be productive,
and \citet[36]{Xing2000stat} concludes that AAB is productive as well.
Thus, these forms should not be handled as  irregular forms, but should be derivable by lexical rules.

### 2024-09-30 chapters/ch05-Analysis.tex
spacing

AAB, A-\textit{yi}-AB, A-\textit{le}-AB, AA-\obj{kan4} and A-\obj{kan4}-\obj{kan4} can also be accounted for by the lexical rules proposed in this section.
They can be analyzed as compounds consisting of a reduplicated monosyllabic verb and another element.
Specifically, AAB, A-\textit{yi}-AB and A-\textit{le}-AB can be considered as the compound of a reduplicated monosyllabic verb (A) and a noun (B).\footnote{
    \citet[64--65]{Huang1984} and \citeauthor{Her1996} (\citeyear[Sec. 2]{Her1996}; \citeyear[Sec. 3.1]{Her2010}) argue that some of these V-O combinations are compounds, some are phrases, and some have dual status (both compounds and phrases).
    Following this approach, AAB, A-\textit{yi}-AB and A-\textit{le}-AB can (also) be considered as the phrasal combination of a reduplicated verb and its object.
}
AA-\obj{kan4} can be regarded as the compound of a reduplicated monosyllabic verb (A) and the verb \obj{kan4} `look',
whereas A-\obj{kan4}-\obj{kan4} is the compound of a monosyllabic verb (A) and the reduplication of \obj{kan4} `look'.
A-\obj{yi}-A-\obj{kan4} is also possible, though rare, presumably also due to its length.
An inquiry in CCL found 55 hits of A-\obj{yi}-A-\obj{kan4}.
A sample is listed in (\ref{ex:AyiAkan}).

>>>>

AAB, A-\textit{yi}-AB, A-\textit{le}-AB, AA-\obj{kan4} and A-\obj{kan4}-\obj{kan4} can also be accounted for by the lexical rules proposed in this section.
They can be analyzed as compounds consisting of a reduplicated monosyllabic verb and another element.
Specifically, AAB, A-\textit{yi}-AB and A-\textit{le}-AB can be considered as the compound of a reduplicated monosyllabic verb (A) and a noun (B).\footnote{
    \citet[64--65]{Huang1984} and \citeauthor{Her1996} (\citeyear[Sec.\,2]{Her1996}; \citeyear[Sec.\,3.1]{Her2010}) argue that some of these V-O combinations are compounds, some are phrases, and some have dual status (both compounds and phrases).
    Following this approach, AAB, A-\textit{yi}-AB and A-\textit{le}-AB can (also) be considered as the phrasal combination of a reduplicated verb and its object.
}
AA-\obj{kan4} can be regarded as the compound of a reduplicated monosyllabic verb (A) and the verb \obj{kan4} `look',
whereas A-\obj{kan4}-\obj{kan4} is the compound of a monosyllabic verb (A) and the reduplication of \obj{kan4} `look'.
A-\obj{yi}-A-\obj{kan4} is also possible, though rare, presumably also due to its length.
An inquiry in CCL found 55 hits of A-\obj{yi}-A-\obj{kan4}.
A sample is listed in (\ref{ex:AyiAkan}).
